General Physics Formula

### 2016-11-09 General Physics Formula/General Physics Formula.tex
New notes in Draft, about a specific function.
Some micellaneous useful physical ponts.

\maketitle
\abstract{
This is a collection of important formulae in Fundamentals of Physics
Extended Version by Halliday and Resnick.
}
\tableofcontents

@@

\paragraph{Rotation matrix}
Active rotation in the counter-clockwise $\theta$:
\begin{equation}
    \left(
    \begin{array}{cc}
        \cos{\theta} & -\sin{\theta} \\
        \sin{\theta} & \cos{\theta} \\
    \end{array}
    \right)
\end{equation}

@@

\begin{align}
    & U_E = \frac{q^2}{2C} \\
    & U_B = \frac{L i^2}{2} \\
    & \omega = \frac{1}{\sqrt{LC}}
\end{align}
Predicting RLC current (\textbf{pp.843 of \cite{book}})

\begin{align}
    & X_C = \frac{1}{\omega_d C} \\
    & X_L = \omega_d L \\
    & V = I X \\
    & Z_\text{impedance} = \text{vector sum of all above} \\
    & Z = \sqrt{R^2+(X_L-X_C)^2}  \text{ for simple RLC circuit}
\end{align}
% \begin{itemize}
%     \item \textbf{Resisitor} $V_R$ is in phase with $I$.
%     \item \textbf{Capacitor} $V_C$ lags $I$ by 90 degree.
%     \item \textbf{Inductor} $V_C$ preceeds $I$ by 90 degree.
% \end{itemize}
\paragraph{Maxwell's Equations} (\textbf{pp.869 of \cite{book}})

\begin{align}
    & \oint \vec{E} \cdot \diff \vec{A} = q_\text{enc}/\varepsilon_0
    \\
    & \oint \vec{B} \cdot\diff\vec{A} = 0 \\
    & \oint \vec{E}\cdot\diff\vec{s} = -\frac{\diff\Phi_B}{\diff t} \\
    & \oint \vec{B}\cdot\diff\vec{s} = 
    \mu_0\varepsilon_0 \frac{\diff\Phi_E}{\diff t} +\mu_0 i_\text{enc}
    \nonumber\\
    & \,= \mu_0 i_d + \mu_0 i_\text{enc}
\end{align}

@@

\paragraph{Photon} (\textbf{pp.1077 ch38 of \cite{book}})
\begin{align}
    & E = h f \\
    & p= \frac{hf}{c} = \frac{h}{\lambda} \\
    & hf = K_\text{max} + \Phi_\text{work function} \\
    & \Delta\lambda = \frac{h}{mc}(1-\cos{\phi})
\end{align}

>>>>

\maketitle
\abstract{
This is a collection of important formulae in Fundamentals of Physics
Extended Version by Halliday and Resnick, and some other formulae from
other sources. Although this was initially intended to be preparation
for GRE physics exam, I found such a review quite useful and will
continue to update this document whenever I found something useful.
}
\tableofcontents

@@

\include{sections/math}

@@

\begin{align}
    & U_E = \frac{q^2}{2C} \\
    & U_B = \frac{L i^2}{2} \\
    & \omega = \frac{1}{\sqrt{LC}}
\end{align}

\textbf{RC Circuit}
\begin{align}
    Q = Q_0 e^{-t/(RC)}
\end{align}
Predicting RLC current (\textbf{pp.843 of \cite{book}})

\begin{align}
    & X_C = \frac{1}{\omega_d C} \\
    & X_L = \omega_d L \\
    & V = I X \\
    & Z_\text{impedance} = \text{vector sum of all above} \\
    & Z = \sqrt{R^2+(X_L-X_C)^2}  \text{ for simple RLC circuit}
\end{align}
\begin{itemize}
    \item \textbf{Resisitor} $V_R$ is in phase with $I$.
    \item \textbf{Capacitor} $V_C$ lags $I$ by 90 degree.
    \item \textbf{Inductor} $V_C$ preceeds $I$ by 90 degree.
\end{itemize}
\paragraph{Maxwell's Equations} (\textbf{pp.869 of \cite{book}})

\begin{defi}[Permittivity = Dielectric Constant]
\nomenclature{Permittivity = Dielectric Constant}{$\varepsilon$, \nomrefpage.}
    $\varepsilon$
\end{defi}
\begin{defi}[Permeability]
\nomenclature{Permeability}{$\mu$, \nomrefpage.}
    $\mu$
\end{defi}
\begin{align}
    & \oint \vec{E} \cdot \diff \vec{A} = q_\text{enc}/\varepsilon_0
    \\
    & \oint \vec{B} \cdot\diff\vec{A} = 0 \\
    & \oint \vec{E}\cdot\diff\vec{s} = -\frac{\diff\Phi_B}{\diff t} \\
    & \oint \vec{B}\cdot\diff\vec{s} = 
    \mu_0\varepsilon_0 \frac{\diff\Phi_E}{\diff t} +\mu_0 i_\text{enc}
    \nonumber\\
    & \,= \mu_0 i_d + \mu_0 i_\text{enc}
\end{align}

@@

\paragraph{de Broglie Waves}
(\href{https://en.wikipedia.org/wiki/Matter_wave}{Wikipedia - Matter
Wave})
\begin{align}
    \lambda &= \frac{h}{p} \\
    p &= \frac{h}{\lambda} = \hbar\frac{2\pi}{\lambda} = \hbar k \\
    p &= \frac{hf}{c} \\
    f &= \frac{E}{h} \\
    E &= hf = \hbar2\pi f = \hbar\omega
\end{align}
\paragraph{Photon} (\textbf{pp.1077 ch38 of \cite{book}})
\begin{align}
    & E = h f \\
    & p= \frac{hf}{c} = \frac{h}{\lambda} \\
    & hf = K_\text{max} + \Phi_\text{work function} \\
    & \Delta\lambda = \frac{h}{mc}(1-\cos{\phi})
\end{align}
